Analysing the factors influencing the wages of the US workforce

### 2024-11-26 paper/paper.qmd
fix reference

library(tidyverse)
library(ggplot2)
library(dplyr)
library(here)
library(reshape2)
library(scales)
library(arrow)
library(knitr)
library(kableExtra)
library(car) 
library(broom) 
```

@@

library(caret)
library(broom)
library(knitr)
library(kableExtra)

@@

# Appendix {-} {#sec-appendix}

>>>>

library(tidyverse)
library(ggplot2)
library(dplyr)
library(here)
library(reshape2)
library(scales)
library(arrow)
library(knitr)
library(kableExtra)
library(car) 
library(broom) 
library(caret)

@@

@@

# Appendix  {#sec-appendix}
